plyranges: a grammar for transforming genomics data

### 2018-04-19 paper.Rmd
ideas for endomorphism section

@@

Finally, we can use `group_by_overlaps` with `summarise` to compute the
total number of reads with in each window.

@@

>>>>

* compute coverage as an example here

@@

Finally, we can use `group_by_overlaps` with `summarise` to compute the
total number of reads within each window.

@@

https://support.bioconductor.org/p/71601/ also useful example?
